Adaptative Computation:\\ An Essay in Memory of John H. Holland

### 2016-02-08 paper.tex
incorporated reviewer suggestions as discussed in phone call.  Added acknowledgments and steph's grant support.  still need a footntoe with date and stating where it will be published.

\begin{abstract}
In this essay we review the work and influence of the late John H. Holland, pioneer in the fields of evolutionary computation, machine learning, and complex systems.  While best known for his invention of \emph{genetic algorithms}, Holland's scientific motivation was much broader:  to develop a general theory of adaptation in complex systems.  We survey Holland's motivation and work with respect to four central themes, and describe how this work has had both broad and deep influence in modern approaches to computer science and complex systems science.  
\end{abstract}

@@

Professor John H. Holland passed away recently in Ann Arbor, MI, where
he had served on the University of Michigan faculty for over 50 years.
John, as he was known universally to his colleagues and students,
leaves behind a long legacy of intellectual achievements.

As a descendant of the cybernetics era, Holland was strongly
influenced by the work of von Neumann, Wiener, Ashby, and Turing, all
of whom viewed computation as a broad, interdisciplinary enterprise.
Thus, Holland became an early proponent of interdisciplinary
approaches to computer science and an active evangelist of what is now
called \emph{computational thinking}, reaching out enthusiastically to
psychologists, economists, physicists, linguists, philosophers, and
pretty much anyone he came in contact with.  As a result, even though
he received what was arguably the world's first computer science
Ph.D. in 1959, his contributions are sometimes better known outside of
computer science than within.

Holland is best known for his invention of \emph{genetic
  algorithms} (GAs), a family of search and optimization methods inspired
by biological evolution.  Since their invention in the 1960s, GAs have
inspired many related methods and led to the thriving subfield of
\emph{evolutionary computation}, with widespread scientific and
commercial applications.  While the mechanisms of GAs are well-known,
they were only one
offshoot of Holland's broader motivation---to develop a general
theory of adaptation in complex systems.

@@

Holland's goal of developing a general theory of adaptation was
spurred both by his early work on computer models of Hebbian learning
\cite{Rochester1956} and his reading of Ronald Fisher's classic book
on integrating genetics with Darwinian selection \cite{Fisher1930}.
As Holland further read extensively in evolutionary biology,
economics, game theory, and control theory, he came to recognize that
adaptation was the most central concept in all these fields.  That is,
these fields all concern populations of agents that must continually
obtain information from uncertain, changing environments and use it in
order to improve performance and enhance the chance of survival.

Moreover, Holland recognized that adaptation must be a continual
open-ended process due to perpetually uncertain and changing
environments.  Thus, adaptive systems never achieve a state of
equilibrium or a final optimum configuration.  This emphasis on
open-ended, non-equilibrium dynamics was in stark contrast with the
mainstream approach (at the time) in all these fields---the belief
that solving for stable equilibrium dynamics was the scientific goal.
Holland's contrary view was that a system in stable equilibrium is
essentially \emph{dead}.

Underlying Holland's theory of adaptation are the following core ideas.

\begin{itemize}
\item{\bf Populations, sampling, and implicit parallelism:} 
  Evolution can be framed as a search that leverages statistics to
  direct population dynamics.  A population can be thought of as a
  parallel sampling of many individuals (from the space of possible
  individuals).  Moreover, that same population can be thought of as
  implicitly sampling a much larger space of \emph{traits} that
  comprise those individuals.  Holland termed this implicit
  large-scale sampling of traits ``implicit parallelism.''
  Evolutionary dynamics biases these samples over time towards
  high-fitness regions of the search space.

\item{\bf Building blocks and recombination:} 
  In a population undergoing adaptation,
  individuals can be decomposed into \emph{building blocks}---sets of
  traits that are the evolutionary ``atoms'' of an individual's
  fitness or performance. (As an example from biology, Holland gives
  the \emph{Krebs cycle}, a core cellular metabolic
  pathway.)   Successful individuals
  are discovered in stages, first by finding useful
  building blocks through stochastic sampling, and over
  time recombining such building blocks to create higher-fitness individuals.

@@

Inspired by Bellman \cite{Bellman1961} and
others, Holland formalized the exploitation-versus-exploration tradeoff
via an idealized ``two-armed bandit'' problem. Given a slot machine
with two arms, each of which has an unknown payoff probability, how
should you allocate trials (pulls) between the arms so as to
maximize your total payoff?   In \cite{Holland1973,Holland1975}
Holland argued that the optimal strategy
allocates trials to the observed best arm at a slightly higher rate than
an exponential function of the trials allocated to the observed worse arm.

@@

The question of balancing exploitation and exploration---how to
optimally allocate trials to different arms based on their observed 
payoffs---now becomes the question of how to optimally sample in the
vast space of possible building blocks, based on their estimated
contribution to fitness.  Of course, evolution deals in populations of
individuals, not building blocks.  There is no {\emph explicit} mechanism for
keeping statistics on how building blocks contribute to fitness. 
Holland's central idea here is that an approximation to
optimal building-block sampling does implicitly occur, as an emergent
property of evolutionary population dynamics.

Several of Holland's early papers (e.g.,
\cite{Holland1962,Holland1973}) and his influential 1975 book
\emph{Adaptation in Natural and Artificial Systems} \cite{Holland1975}
developed a general, formal setting in which these ideas could be
expressed mathematically.  It was this formalization that led to the
invention of genetic algorithms, which featured stochastic
population-based search, as well as crossover between individuals as a
critical operation that allowed successful building blocks to be
recombined and tested in new contexts.  Holland's aim, however, was
more general than a new class of algorithms---his goal was an
interdisciplinary theory of adaptation, one that would inform biology, 
say, as much as computer science \cite{Christiansen1998}.  The later, successful application of
genetic algorithms to real-world optimization and learning tasks was,
for Holland, just icing on the cake.

@@

Holland's second key contribution was describing a computational
mechanism, the \emph{learning classifier
  system}~\cite{Holland1986,Holland1977}, to illustrate how a cognitive system could
iteratively build up a detailed and hierarchical model of its
environment to enhance survival.  The key learning elements of this method, the
\emph{bucket-brigade} algorithm combined with a genetic algorithm, presaged many of the ideas in modern reinforcement
learning.

@@

%Finally, new rules for the population are discovered by a genetic
%algorithm, using the strength of rules as a fitness function.
%Classifier systems are fairly complex architectures, with learning
%occurring at multiple time scales.  
Although Holland proposed classifier systems as 
an executable theory of inductive processes in cognition, other researchers took it further, 
%other researchers took the
%computational system more seriously
applying it to areas as diverse as poker-playing \cite{Smith1980},
control of gas pipeline transmission \cite{Goldberg1983}, and modeling
the stock market \cite{Palmer1994}.  (See Ref.~\cite{Booker1989} for
more details about practical applications of classifier systems.)
Today, other reinforcement learning methods are more popular for
real-world decision and control problems, but classifier systems can
perhaps be thought of as an early stage-setting method that helped
build the foundations for later approaches.

@@

Holland's work focused on {\emph exploratory} models---those that explore basic principles and
mechanisms, even if they do not make specific or detailed
predictions.  Such models can show generically how certain behaviors
could be produced.  Holland pioneered a style of modeling that has
come to be known as ``individual-based'' or ``agent-based,'' in which
every component of a system is represented explicitly---e.g., every
trader in a stock market system or every cell in an immune system
model---and has a dynamic internal state. In such models, each agent has
its own behavior rules, which it can modify over time through learning.  In
order to capture the behavior of systems under spatial
constraints, these models are often defined over spatial structures
such as networks or simple grids.

@@

The emphasis on exploratory models to build intuitions was an
important theme of Holland's work, and he often quoted Eddington's
remark on the occasion of the first experimental test of Einstein's
theory of relativity: ``The contemplation in natural science of a wider
domain than the actual leads to a far better understanding of the
actual'' \cite{Eddington1927}.

%It should be noted that Holland's view of modeling is by no means
%typical.  For example, a textbook on computational modeling offers
% the following definition: ``Modeling is the application
%of methods to analyze complex, real-world problems in order to make
%predictions about what might happen with various actions''
%\cite{Shiflet2014}.   This perspective rules out the
%kind of exploratory modeling that Holland was most interested in.

@@

Holland was interested in a broad array of adaptive systems---immune
systems, ecologies, financial markets, cities, and the brain---systems
that are \emph{complex}.  In the early 1980s, he teamed up with a small
group of scientists, primarily physicists with a sprinkling of
economists and biologists, to discuss what properties this wide swath of systems
have in common.  The discussions helped define the intellectual mission
of the Santa Fe Institute (SFI), the first institution dedicated to
developing a science of complexity, and the many others that followed.
% [add in how many complexity
%  institutes there are worldwide and which others John played a hand
%  in. MM says: Do we really need that?]  
Holland brought to these discussions his lifelong study of
adaptation and a reminder that serious theories about complexity would
need to look deeper than phenomenological descriptions but also
account for the `how' and `why' of these systems.
%describing phenomena like chaos, power laws, and ONE MORE, and acoount for the

As the discussions matured, a consensus developed about the basic
elements of complex systems, which are: (1) 
%complex systems are 
composed of many
components with nonlinear interactions; (2) 
%such systems
%are 
characterized by complex \emph{emergent} behavior, exhibiting
higher-order patterns; (3) 
%such systems 
operating at multiple (and often
% interacting? 
nested) spatial and temporal scales, with some behavior being
conserved across all scales and other behaviors changing at different
scales, and (4) 
%these systems exhibit 
adaptive, with 
behavioral rules continually adjusting through evolution and learning.  Although this
is far from a formal definition of complex systems, most people
working in the field today are interested in systems that have these
properties.

@@

The SFI Artificial Stock Market project \cite{Arthur1997,Palmer1994}
developed an exploratory model in which rational
traders were replaced by \emph{adaptive} traders---those who learn to
forecast stock prices over time.  The model tested for the
emergence of different trading strategies, including
\emph{fundamental}, \emph{technical}, or \emph{uninformed}
strategies. The simulated market with adaptive trading agents was run
many times, and the dynamics of price and trading volumes were
compared to observed patterns in real markets.  Holland and his
collaborators found that the model's dynamics replicated several
features of real-life markets.

@@

@@

Holland's later books, \emph{Emergence} \cite{Holland2000},
\emph{Signals and Boundaries} \cite{Holland2012}, and
\emph{Complexity: A Very Short Introduction} \cite{Holland2014} show how the
theories of adaptation that Holland developed during the earlier part
of his career fit into the larger landscape of complex systems
research.  Holland's focus on understanding the mechanisms by which complex patterns emerge and change,
rather than simply characterizing the patterns themselves (e.g.,
describing chaotic attractors or power laws), reflected his
determination to get to the heart of complex adaptive systems.
This determination represents the best of science.  Holland's
willingness to tackle the hardest questions, develop his own
formalisms, and use mathematics to provide insight sets a high bar for
scientists in all disciplines.
%to whch we
%all should aspire.

@@

John Holland was unusual in his ability to absorb the essence of other
disciplines, articulate grand overarching
principles, and them back them up with computational mechanisms and
mathematics.  Unlike most researchers, Holland moved seamlessly among these
three modes of thinking, developing models that were years ahead of their time.  A
close reading of his work reveals the antecedents of many ideas prevalent in
machine learning today, e.g., reinforcement, learning in non-Markovian
environments and active learning.   His seminal genetic algorithm
spawned the field of evolutionary computation, and his insights
and wisdom helped define what are now referred to as the
\emph{sciences of complexity}.

@@

>>>>

\begin{abstract}
This essay reviews the work and influence of the late John H. Holland,
pioneer in the fields of evolutionary computation, machine learning,
and complex systems.  While best known for his invention of
\emph{genetic algorithms}, Holland's scientific motivation was much
broader:  to develop a general theory of adaptation in complex
systems.  We survey Holland's motivation and research with respect to
four central themes, describing his broad and deep influence on modern approaches to computer science and complex systems science.  
\end{abstract}

@@

In Aug. 2015, Professor John H. Holland passed in Ann Arbor, MI, where
he had served on the University of Michigan faculty for over 50 years.
John, as he was known universally to his colleagues and students,
leaves behind a long legacy of intellectual achievements.

As a descendant of the cybernetics era, Holland was 
influenced by the work of von Neumann, Wiener, Ashby, and Turing, all
of whom viewed computation as a broad, interdisciplinary enterprise.
Thus, Holland became an early proponent of interdisciplinary
approaches to computer science and an active evangelist of what is now
called \emph{computational thinking}, reaching out enthusiastically to
psychologists, economists, physicists, linguists, philosophers, and
pretty much anyone he came in contact with.  As a result, even though
he received what was arguably one of the world's first computer
science
% SF softened the claim here after reading the comments section on the blog.
Ph.D. degrees in 1959\cite{London2003}, his contributions are sometimes better known outside of
computer science than within.

Holland is best known for his invention of \emph{genetic
  algorithms} (GAs), a family of search and optimization methods inspired
by biological evolution.  Since their invention in the 1960s, GAs have
inspired many related methods and led to the thriving subfield of
\emph{evolutionary computation}, with widespread scientific and
commercial applications.  Although the mechanisms of GAs are well-known,
they were only one
offshoot of Holland's broader motivation---to develop a general
theory of adaptation in complex systems.

@@

Holland's goal of developing a general theory of adaptation was
spurred both by his early work on computer models of Hebbian learning
\cite{Rochester1956} and his reading of Ronald Fisher's classic book
on integrating genetics with Darwinian selection \cite{Fisher1930}.
As Holland read further in evolutionary biology,
economics, game theory, and control theory, he recognized that
adaptation is central to all these fields.  That is,
these fields all concern populations of agents that must continually
obtain information from uncertain, changing environments and use it 
to improve performance and enhance the chance of survival.

Holland also recognized that adaptation must be a continual
open-ended process due to perpetually uncertain and changing
environments.  In his view, adaptive systems never achieve a state of
equilibrium or a final optimum configuration.  This emphasis on
open-ended, non-equilibrium dynamics was in stark contrast with the
mainstream approach (at the time) in all these fields---the belief
that solving for stable equilibrium dynamics was the scientific goal.
Holland's contrary view was that a system in stable equilibrium is
essentially \emph{dead}.

Underlying Holland's theory of adaptation are the following core ideas:

\begin{itemize}
\item{\bf Populations, sampling, and implicit parallelism:} 
  Evolution is a form of search that leverages statistics to
  direct population dynamics.  Initially, the population is an 
 independent sample of many individuals (from the space of all possible
  individuals), and over time the sample is increasingly biased
  towards the high-fitness regions of the search space.  In addition,
the population can be viewed as an
  implicit sample of the much larger space of \emph{traits} that
  comprise those individuals.  Holland termed this implicit
  large-scale sampling of traits ``implicit parallelism.''
  Evolutionary dynamics biases these samples over time towards
  high-fitness regions of the search space.

\item{\bf Building blocks and recombination:} 
  In a population undergoing adaptation,
  individuals can be decomposed into \emph{building blocks}---sets of
  traits that are the evolutionary ``atoms'' of an individual's
  fitness or performance. (As an example from biology, Holland often mentioned
  the \emph{Krebs cycle}, a core cellular metabolic
  pathway that is highly conserved across living systems.)   Successful individuals
  are discovered in stages, first by finding useful
  building blocks through stochastic sampling, and over
  time recombining them to create higher-fitness individuals out of
  more complex building blocks.

@@

Inspired by Bellman \cite{Bellman1961} and
others, Holland formalized the exploitation-versus-exploration tradeoff
as an idealized ``two-armed bandit'' problem. Given a slot machine
with two arms, each of which has an unknown payoff probability, how
should you allocate trials (pulls) between the arms so as to
maximize your total payoff?   In \cite{Holland1973,Holland1975}
Holland argued that the optimal strategy
allocates trials to the observed best arm at a slightly higher rate than
an exponential function of the trials allocated to the observed worse arm.

@@

The question of balancing exploitation and exploration---how to
optimally allocate trials to different arms based on their observed 
payoffs---now becomes the question of how to optimally sample in the
vast space of possible building blocks, based on their estimated
contribution to fitness.  Of course, evolution deals in populations of
individuals, not building blocks.  There is no \emph{explicit} mechanism that
keeps statistics on how building blocks contribute to fitness. 
Holland's central idea here is that an approximation to
optimal building-block sampling occurs implicitly, as an emergent
property of evolutionary population dynamics.

Several of Holland's early papers (e.g.,
\cite{Holland1962,Holland1973}) and his influential 1975 book
\emph{Adaptation in Natural and Artificial Systems} \cite{Holland1975}
developed a general, formal setting in which these ideas could be
expressed mathematically.  It was this formalization that led to the
invention of genetic algorithms, which featured stochastic
population-based search, as well as crossover between individuals as a
critical operation that allows successful building blocks to be
recombined and tested in new contexts.

% Reviewer 3: I'd be careful with anything relating to the building block hypothesis (that recombination is successful by combining building blocks). How recombination really works and what it serves to seems to be little understood both in genetic algorithms and in biology. In the genetic algorithms literature, there is at least as many negative evidence for the building block hypothesis as support, including a well-known paper by the authors.

Holland's aim, however, was
more general than a new class of algorithms---his goal was an
interdisciplinary theory of adaptation, one that would inform biology, 
say, as much as computer science \cite{Christiansen1998}.  The later, successful application of
genetic algorithms to real-world optimization and learning tasks was,
for Holland, just icing on the cake.  
This broader view of adaptation
has inspired many, and engendered criticism
from others, leading to spirited intellectual debates and
controversies.  Most controversial is the extent to which it can be
demonstrated, either empirically or mathematically, that the behavior
of adaptive systems is actually governed by these principles.
Regardless of one's position on this question, the ideas are compelling
and provide a set of unifying concepts for thinking about adaptation.
%as follows:
%Underlying Holland's theory of adaptation are the following core ideas:

@@

Holland's second key contribution was describing a computational
mechanism, the \emph{learning classifier
  system}~\cite{Holland1986,Holland1977}, to illustrate how a cognitive system could
iteratively build up a detailed and hierarchical model of its
environment to enhance survival.  The key learning elements of this method, the
\emph{bucket-brigade} algorithm combined with a genetic algorithm, presaged many of the ideas in modern reinforcement
learning, notably the temporal-difference methods introduced by
Sutton and Barto~\cite{SuttonAndBarto1990}.

@@

%Finally, new rules for the population are discovered by a genetic
%algorithm, using the strength of rules as a fitness function.
%Classifier systems are fairly complex architectures, with learning
%occurring at multiple time scales.  
Although Holland proposed classifier systems as 
an executable theory of inductive processes in cognition, other researchers took it further, 
%other researchers took the
%computational system more seriously
applying it to areas as diverse as poker-playing \cite{Smith1980},
control of gas pipeline transmission \cite{Goldberg1983}, and modeling
the stock market \cite{Palmer1994}.  (See Ref.~\cite{Booker1989} for
more details about practical applications of classifier systems.)
Today, other reinforcement learning methods are more popular for
real-world decision and control problems, but classifier systems can
perhaps be thought of as an early stage-setting method that
foreshadowed these later approaches.

@@

Holland's work focused on \emph{exploratory} models---those that explore basic principles and
mechanisms, even if they do not make specific or detailed
predictions\cite{Holland1995}.  Such models can show generically how certain behaviors
could be produced.  Holland pioneered a style of modeling that has
come to be known as ``individual-based'' or ``agent-based,'' in which
every component of a system is represented explicitly---e.g., every
trader in a stock market system or every cell in an immune system
model---and has a dynamic internal state. In such models, each agent has
its own behavior rules, which it can modify over time through learning.  In
order to capture the behavior of systems under spatial
constraints, these models are often defined over spatial structures
such as networks or simple grids.

@@

The emphasis on exploratory models to build intuitions was an
important theme of Holland's work, and he often quoted Eddington's
remark on the occasion of the first experimental test of Einstein's
theory of relativity: ``The contemplation in natural science of a wider
domain than the actual leads to a far better understanding of the
actual'' \cite{Eddington1927}.
Holland's view of modeling was by no means
typical.  As just one example of the prevailing view that models are
for predicting: 
%For example, a textbook on computational modeling offers
% the following definition: 
``Modeling is the application
of methods to analyze complex, real-world problems in order to make
predictions about what might happen with various actions''
\cite{Shiflet2014}.   This perspective rules out the
kind of exploratory modeling that interested Holland the most.

@@

Holland was interested in a broad array of adaptive systems---immune
systems, ecologies, financial markets, cities, and the brain---systems
that are \emph{complex}.  In the early 1980s, he teamed up with a small
group of scientists, primarily physicists with a sprinkling of
economists and biologists, to discuss what properties this wide swath of systems
have in common.  The discussions helped define the intellectual mission
of the Santa Fe Institute (SFI), the first institution dedicated to
developing a science of complexity, as well as the other complexity institutes that followed.
% [add in how many complexity
%  institutes there are worldwide and which others John played a hand
%  in. MM says: Do we really need that?]  
Holland brought to these discussions his lifelong study of
adaptation and a reminder that serious theories about complexity would
need to look deeper than phenomenological descriptions but also
account for the `how' and `why' of these systems.
%describing phenomena like chaos, power laws, and ONE MORE, and acoount for the

As the discussions matured, a consensus developed about the basic
elements of complex systems, which are: (1) 
%complex systems are 
composed of many
components with nonlinear interactions; (2) 
%such systems
%are 
characterized by complex \emph{emergent} behavior, exhibiting
higher-order patterns; (3) 
%such systems 
operating at multiple (and often
% interacting? 
nested) spatial and temporal scales, with some behavior 
conserved across all scales and other behaviors changing at different
scales, and (4) 
%these systems exhibit 
adaptive, with 
behavioral rules continually adjusted through evolution and learning.  Although this
is far from a formal definition of complex systems, most people
working in the field today are interested in systems that have these
properties.

@@

The SFI Artificial Stock Market project \cite{Arthur1997b,Palmer1994}
developed an exploratory model in which rational
traders were replaced by \emph{adaptive} traders---those who learn to
forecast stock prices over time.  The model tested for the
emergence of different trading strategies, including
\emph{fundamental}, \emph{technical}, or \emph{uninformed}
strategies. The simulated market with adaptive trading agents was run
many times, and the dynamics of price and trading volumes were
compared to observed patterns in real markets.  Holland and his
collaborators found that the model's dynamics replicated several
features of real-life markets.

@@

%Reviewer 3It seems to me that the essay could stress even more that Holland was interested in "open ended systems" and that,  ironically,   as genetic algorithms were turned into static function optimizers these "next generation evolutionary algorithms" lost the adaptive properties that Holland valued and emphasized.     We still have very little idea about how to build truly open ended systems.

@@

Holland's later books, \emph{Emergence} \cite{Holland2000},
\emph{Signals and Boundaries} \cite{Holland2012}, and
\emph{Complexity: A Very Short Introduction} \cite{Holland2014} show how the
theories of adaptation that Holland developed during the earlier part
of his career fit into the larger landscape of complex systems
research.  In these works he especially emphasized the open-ended
nature of complex systems, where change and adaptation are
continual, systems co-evolve with each other, and ecological niches arise
and decay spontaneously depending on resource availability and competition..

%i thnk you left out a major  theme in john: the role of the concept of niche.
 % for example, i think that he  was so interested in flows.  because a niche
% can be thought of as a pattterns of flows.  and ibelfeve -one of his
% major goal  ofor ECHO was to study   niche formation and structure 
% did yolu knolw that af\ef the bach gtoujp  \faded we stArted  A group 
% dedicted to zstudyung nichrd ijn all  thire guiidee, i/with john, nmercdes, 
% scott, mi\\chael cohen ,evan ecnomo (a rackam fcfelw) , and me as the core,
%  wiyth visits by;\mike gordon, bob savitn ]marjk newman maria riolo,ed askerville, etc, 
% as far as i can tell, we ]met on avg about 1/mon from  oct 200 - feb
% 2012.

Holland's focus on understanding the mechanisms by which complex patterns emerge and change,
rather than simply characterizing the patterns themselves (e.g.,
describing chaotic attractors or power laws), reflected his
determination to get to the heart of complex adaptive systems.
This determination represents the best of science.  Holland's
willingness to tackle the hardest questions, develop his own
formalisms, and use mathematics to provide insight sets a high bar for
scientists in all disciplines.
%to whch we
%all should aspire.

@@

John Holland was unusual in his ability to absorb the essence of other
disciplines, articulate grand overarching
principles, and then back them up with computational mechanisms and
mathematics.  Unlike most researchers, Holland moved seamlessly among these
three modes of thinking, developing models that were years ahead of their time.  A
close reading of his work reveals the antecedents of many ideas prevalent in
machine learning today, e.g., reinforcement, learning in non-Markovian
environments and active learning.   His seminal genetic algorithm
spawned the field of evolutionary computation, and his insights
and wisdom helped define what are now referred to as the
\emph{sciences of complexity}.

@@

\section{Acknowledgments}

The authors thank L. Booker, R. Riolo, K. Winter, and the anonymous
reviewers for their careful reading of the manuscript and many helpful
suggestions.  SF gratefully acknowledges the partial support of NSF
(NeTS 1518878, CNS 1444500), DARPA (FA8750-15-C-0118), 
Air Force Office of Scientific Research (FA8750-15-2-0075), and the Santa Fe Institute.
